\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome5}
\usepackage[hidelinks,pdfnewwindow=true]{hyperref}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-3pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.00\textwidth}[t]{l@{\extracolsep{\fill}}r}
      #1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-9pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\LARGE \scshape {Avanish Gupta}} \\
    \vspace{0.1cm}
    \href{https://www.linkedin.com/in/avanish-gupta/}{\raisebox{-0.2\height}\faLinkedin\ LinkedIn} ~
    \href{https://github.com/Avanish-Gupta-CSE}{\raisebox{-0.2\height}\faGithub\ GitHub} ~
    \raisebox{-0.1\height}\faPhone\ +91 8107432468 ~ 
    \href{mailto:avanish.gupta.official1@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ avanish.gupta.official1@gmail.com}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{PROFESSIONAL SUMMARY}
\resumeItemListStart
    \resumeItem{Full Stack MERN Developer with \textbf{1.5+ Years} of experience building production-grade web applications using \textbf{React.js}, \textbf{Node.js}, \textbf{Express.js}, and \textbf{MongoDB}, with proficiency in cross-team development and cloud deployments.}
\resumeItemListEnd

%-----------TECHNICAL SKILLS-----------
\section{TECHNICAL SKILLS}
\resumeItemListStart
    \resumeItem{\textbf{MERN Stack}{: MongoDB, Express.js, React.js, Node.js.}}
    \resumeItem{\textbf{Languages}{: JavaScript, TypeScript.}}
    \resumeItem{\textbf{Libraries \& Frameworks}{: Redux Toolkit, React Router, PrimeReact, React Hook Form, TailwindCSS, Vite, Yup, Axios.}}
    \resumeItem{\textbf{Databases \& Search}{: MongoDB, PostgreSQL, Elasticsearch, MySQL.}}
    \resumeItem{\textbf{Cloud \& DevOps}{: AWS (S3, EKS, ECR, SES), Azure DevOps, Docker, Kubernetes, CI/CD Pipelines.}}
    \resumeItem{\textbf{Tools \& Testing}{: Git, Postman, Keycloak, Jest, React Testing Library, Kibana.}}
\resumeItemListEnd

%-----------WORK EXPERIENCE-----------
\section{WORK EXPERIENCE}
\resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{Berkadia} $|$ Bengaluru, IN}
        {\href{https://drive.google.com/file/d/1yrVaOmV1J4laQjglxUJJJVH6zrVVLhhf/view}{\textbf{Certificate} \faExternalLink*}}
    \resumeProjectHeading
        {\textbf{Associate Software Engineer}}{June 2024 -- Present}

        \resumeProjectHeading
            {\textit{ReservesAI -- AI-Powered Document Processing}}{\textit{ongoing}}
        \resumeItemListStart
            \resumeItem{Developing an AI-powered document processing platform using \textbf{React 19}, \textbf{Node.js}, and \textbf{Express}, integrating \textbf{Azure Document Intelligence} and IDP services for automated data extraction from Reserve Request Letters.}
            \resumeItem{Implemented async job processing with \textbf{WebSocket}, built a test harness for bulk validation, and deployed via \textbf{CI/CD pipelines} using \textbf{Azure DevOps} with \textbf{Docker} and \textbf{Kubernetes (EKS)}.}
        \resumeItemListEnd

        \resumeProjectHeading
            {\textit{DMS -- Document Management System}}{}
        \resumeItemListStart
            \resumeItem{Built a Document Management System using \textbf{React 18}, \textbf{TypeScript}, \textbf{Redux Toolkit}, and \textbf{PrimeReact}, featuring document upload, advanced search, bulk operations, and recycle bin for loan servicing workflows.}
            \resumeItem{Designed \textbf{Node.js/Express} REST APIs with \textbf{PostgreSQL}, \textbf{Elasticsearch}, and \textbf{AWS S3} for document storage, integrating \textbf{Keycloak} SSO and \textbf{OpenFGA} for fine-grained role-based authorization across document classes.}
        \resumeItemListEnd

        \resumeProjectHeading
            {\textit{CMS -- Cash Management Service}}{}
        \resumeItemListStart
            \resumeItem{Utilized \textbf{Microservices} to create \textbf{CQRS} based workflows and implemented schema migrations using \textbf{Elasticsearch}, while designing \textbf{REST APIs} using \textbf{Node.js} and \textbf{TypeScript}, with email notifications via \textbf{Amazon SES}.}
            \resumeItem{Developed interactive dashboards using \textbf{React.js} with advanced filters, search, and sorting, utilizing \textbf{Redux} for state management, and achieved \textbf{85\%+} code coverage using \textbf{Jest} and \textbf{React Testing Library}.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{STMicroelectronics Pvt. Ltd.} $|$ Gr. Noida, IN}
        {\href{https://drive.google.com/file/d/1wfKMSeUOJrb3yKr8ekMJOihSBozopkU0/view}{\textbf{Certificate} \faExternalLink*}}
    \resumeProjectHeading
        {\textbf{Project Trainee / SDE Intern}}{August 2023 -- May 2024}
        \resumeItemListStart
            \resumeItem{Built the \textbf{eRFP-NPI} application from the ground up, managing Technical Gap Analysis (TGA) and a product portfolio of \textbf{500+} semiconductor quotations for \textbf{20+} external manufacturing partners, slashing manual processing time by \textbf{70\%}.}
            \resumeItem{Implemented low-level modules and relational schemas to support \textbf{1 million+} price-quote records, boosting complex-query performance by \textbf{45\%} and maintaining \textbf{99.8\%} data integrity.}
            \resumeItem{Developed scalable services in \textbf{NodeJS} and dynamic UI dashboard in \textbf{ReactJS} to serve \textbf{200+} concurrent users within \textbf{300 ms} average API response times.}
            \resumeItem{Resolved \textbf{30+} security findings using \textbf{BMC Helix} from the RMIS audit for FY 23–24—eliminating all critical and high-severity issues to achieve a \textbf{100\%} pass rate on follow-up penetration tests.}
            \resumeItem{Implemented delivery pipelines with \textbf{Jenkins CI/CD} (cutting deploy time by \textbf{50\%}), managed \textbf{100+} Git branches, scheduled \textbf{50+} batch jobs via TWS, and implemented BDD in ALM to raise automated test coverage to \textbf{90\%}.}
        \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Codeial - Social Media Portfolio}}
        {\href{https://codeial-social-app-avanish-gupta-cse.vercel.app/login}{\textbf{Live} \faExternalLink*} $|$ \href{https://github.com/Avanish-Gupta-CSE/Codeial-Social_App}{\textbf{GitHub} \faGithub}}
        \resumeItemListStart
            \resumeItem{Built Codeial, a Git-managed social platform for programmers, leveraging \textbf{ReactJS}, \textbf{Redux}, \textbf{Material-UI} and \textbf{OAuth} to deliver a secure, modular and visually consistent UI.}
            \resumeItem{Implemented a scalable backend using \textbf{Node.js}, \textbf{Express}, \textbf{MongoDB} (via Mongoose) and MockBee to simulate RESTful APIs for authentication, posts, bookmarks, likes, search, and profile management.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{ShopKicks - E-commerce Platform}}
        {\href{https://super-kicks.netlify.app/}{\textbf{Live} \faExternalLink*} $|$ \href{https://github.com/Avanish-Gupta-CSE/E-commerce-website-Super-Kicks}{\textbf{GitHub} \faGithub}}
        \resumeItemListStart
            \resumeItem{Devised a dynamic storefront with \textbf{ReactJS}, \textbf{React Router}, \textbf{Redux Toolkit}, and \textbf{Tailwind CSS}, implementing \textbf{JWT} authentication, \textbf{Fuse.js} instant search, and user dashboards for cart and wishlist management.}
            \resumeItem{Engineered a robust API layer using \textbf{Node.js}, \textbf{Express}, and \textbf{MongoDB} (via Mongoose), integrating \textbf{Stripe} for secure payments and \textbf{Passport.js} for role-based access control across checkout, order history, and address management.}
        \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart
    \resumeSubheading
        {KIIT Deemed to be University, Bhubaneswar}{CGPA: \textbf{9.60}}
        {B.Tech. - Computer Science Engineering}{2020 - 2024}
    \resumeSubheading
        {Bhagat Public Sr. Sec. School, Kota}{Percentage: \textbf{77.40\%}}
        {Intermediate}{}
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
\resumeItemListStart
    \resumeItem{Received \textbf{HI5 Award} for exceptional project contributions at Berkadia.}
    \resumeItem{Achieved \textbf{Runner-Up Award} at the STMicroelectronics Hackathon 2024.}
\resumeItemListEnd

%-----------INTERESTS-----------
\section{INTERESTS}
\small{• Badminton, Fitness, Cycling.}

\end{document}